Extended Data

### 2022-03-10 doc/manuscript/Dow_Extended_Data.Rmd
update text & figure captions for issue #123

##figures
EDF_map = "Extended Data Figure 1" 
EDF_growth_curves_all = "Extended Data Figure 2"  
EDF_climwin = "Extended Data Figure 3"
EDF_pheno_all = "Extended Data Figures 4-5"
EDF_pheno_Tmax_climwin = "Extended Data Figure 4"
EDF_pheno_Tmax_AprilMay = "Extended Data Figure 5"
EDF_tree_ring_figs= "Extended Data Figure 6-7"
EDF_tree_rings_TMIN = "Extended Data Figure 6"
EDF_tree_rings_TMAX_extended = "Extended Data Figure 7"

@@

![**Extended Data Figure 5 | Response of stem growth timing and rates to April mean maximum temperature ($T_{max}$) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** Shown are relationships between April $T_{max}$ and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ declined significantly with April $T_{max}$, with the exception of $DOY_{25}$ for ring-porous species at SCBI. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_april.png){ width=90% }

>>>>

##figures
EDF_map = "Extended Data Figure 1" 
EDF_growth_curves_all = "Extended Data Figure 2"  
EDF_climwin = "Extended Data Figure 3"
EDF_pheno_all = "Extended Data Figures 4-5"
EDF_pheno_Tmax_climwin = "Extended Data Figure 4"
EDF_pheno_Tmax_month = "Extended Data Figure 5"
EDF_tree_ring_figs= "Extended Data Figure 6-7"
EDF_tree_rings_TMIN = "Extended Data Figure 6"
EDF_tree_rings_TMAX_extended = "Extended Data Figure 7"

@@

![**Extended Data Figure 5 | Response of stem growth timing and rates to mean maximum temperatures ($T_{max}$) for the month most closely corresponding to the spring critial temperature window (CTW) for ring- and diffuse-porous speces at the Smithsonian Conservation Biology Institute (SCBI) and Harvard Forest.** CTW was defined as the period over which $T_{max}$ was most strongly correlated with the day of year on which 25% of annual growth was achieved ($DOY_{25}$; `r EDT_phenology_parameters`, `r EDF_climwin`), and the most closely corresponding month was determined as that with the greatest number of days within the CTW. Shown are relationships between montlhy $T_{max}$ and days of the year on which 25%, 50%, and 75% total stem growth were achieved ($DOY_{25}$, $DOY_{50}$, $DOY_{75}$, respectively; first row); the length of the peak growing season ($L_{pgs}$; second row); maximum growth rate ($g_{max}$; third row); and total seasonal radial stem growth ($\Delta DBH$; fourth row). Posterior predictions of each variable that did not include zero are represented with solid lines, while those that do include zero use dotted lines. 95% credible intervals are represented by bands. For both species groups at both sites, $DOY_{25}$, $DOY_{50}$, and $DOY_{75}$ declined significantly with April $T_{max}$, with the exception of $DOY_{25}$ for ring-porous species at SCBI. Dots represent growth parameter values for individual tree-year combinations, which were derived by fitting a five-parameter logistic growth model to dendrometer band data.](tables_figures/pheno_Tsensitivity_combo_patchwork_month.png){ width=90% }

### 2022-03-10 doc/manuscript/Dow_manuscript_Nature.Rmd
update text & figure captions for issue #123

To ensure that patterns were robust under an alternative definition of CTW, and to parallel the monthly time windows used in our tree-ring analysis (detailed below; Fig. `r tree_rings`, `r EDF_tree_ring_figs`), we also ran analyses where we fixed the CTW to be the month of April.
This was consistent with the periods identified by *climwin* for ring- and diffuse porous species groups at both sites, all of which included all or part of April (`r  EDT_phenology_parameters`).

>>>>

To ensure that patterns were robust under an alternative definition of CTW, and to parallel the monthly time windows used in our tree-ring analysis (detailed below; Fig. `r tree_rings`, `r EDF_tree_ring_figs`), we also ran analyses where we fixed the CTW identified by *climwin* to be the month with the most days in the CTW (`r  EDT_phenology_parameters`) each critical window. 
The months identified were March and April for ring- and diffuse-porous species at SCBI, respectively, and April and May for ring- and diffuse-porous species at Harvard Forest, respectively.
